
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}


\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]


\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Large Rohith Raju}} & Email : \href{mailto:meetrohithkraju@gmail.com}{meetrohithkraju@gmail.com}\\
    Mobile : +46 073-703-9412 \\
  Linkedin : \href{https://linkedin.com/in/rohith-raju-11250a19b}{Rohith Raju} &Github : \href{https://github.com/rohith-raju}{Rohith-Raju}
\end{tabular*}


\section{Summary}
Software Engineer. Google Summer of Code contributor at CNCF Falco and Speaker at Kubecon Chicago. Currently pursuing master's in
computer science at Linkoping University.

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Linkoping University}{Linkoping, Sweden}
      {Computer Science, Master's Programme - 6MICS}{Aug. 2024 -- Aug. 2026}
    \resumeSubheading
      {Reva University}{Bangalore, India}
      {Bachelor's in Computer Science and Engineering   GPA: 8.75/10 }{Aug. 2019 -- July. 2023}
    \resumeSubheading
      {Deeksha Pre University}{Bangalore, India}
      {Pre University PCMC : First class }{Aug. 2017 -- Feb. 2019}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
  {Google summer of code at CNCF Falco}{Remote}
  {Open source developer} {May 2023 - September 2023 4 mos}
  \resumeItemListStart
  \resumeItem{Building Falco Playground using Wasm}
  {Contributed to the development of a Falco rules playground as part of the Google Summer of Code program. Worked on creating a web-app without a backend, leveraging WebAssembly. 
  Collaborated closely with a mentor to take the project from concept to completion, providing a dedicated environment for writing and experimenting with Falco rules.}
  \resumeItem{Skills:}
  {C++, Cmake, React, Typescript, WebAssembly, Github Actions, Kernel}
  \resumeItemListEnd  


  \resumeSubheading
  {Motorola Solutions}{Bangalore, India}
  {Internhip Trainee }{July 2022 - December 2022 6 mos}
  \resumeItemListStart
  \resumeItem{Messaging Team}
  {Worked on spring boot microservices and internal tools, used for mission-critical push-to-talk communications.}
  \resumeItem{Skills:}
  {Linux , Docker , Jira , Springboot basics}
\resumeItemListEnd
   

    \resumeSubheading
      {Betsol}{Bangalore, India}
      {Software Engineering Intern}{Jun 2022 - July 2022 1 mos}
      \resumeItemListStart
        \resumeItem{Docker Containerization}
          {Containerized swiftcode Repository which uses play framework to deploy the application using Docker}
        \resumeItem{Skills:}
        { Docker }
      \resumeItemListEnd

    \resumeSubheading
      {PawsNme}{Bangalore, India}
      {Web Developer Intern}{Nov 2020 - Oct 2021 1yr}
      \resumeItemListStart
        \resumeItem{Node Script}
          {Revised a method to transfer data from an xlsx file into the database, streamlining the process. 
          Resolved various bugs and challenges associated with backend endpoints, ensuring smooth functionality and enhanced user experience.}
        \resumeItem{Skills:}
        { Node.Js , Express }
      \resumeItemListEnd

    \resumeSubheading
      {Ninjaas Internet - Retail and eCommerce}{Bangalore,India}
      {Web Developer Intern}{Aug 2021 - Sep 2021 2 mos}
      \resumeItemListStart
        \resumeItem{Tellack}
          {Tellack is script built with node to move all the chat data from Telegram to Slack.}
          \resumeItem{Skills:}
          { Node.Js  }    
      \resumeItemListEnd
          
  \resumeSubHeadingListEnd

\section{Open Source Contributions}  
\resumeSubHeadingListStart
\resumeSubheading
  {Falco Security }{Bangalore, India}
  {Contributor | \href{https://github.com/falcosecurity}{https://github.com/falcosecurity}}{April 2023 - present}
  \resumeItemListStart
  \resumeItem{Flaco Libs} 
   {Falco is a cloud-native security tool designed for Linux systems. It employs custom rules on kernel events, which are enriched with container and Kubernetes metadata, to provide real-time alerts.
    My contributions involed adding addtional syscalls to the core falco libs repository.}
\resumeItemListEnd
  \resumeSubheading
  {Layer5}{Bangalore, India}
  {Member/Contributor | \href{https://github.com/meshery}{https://github.com/meshery} }{May 2022 - December 2022}
  \resumeItemListStart
  \resumeItem{Meshery}
  {Meshery is the cloud native management plane offering lifecycle, configuration, 
  and performance management of Kubernetes, service meshes, and your workloads. 
  My contribution involved improving the UI/UX of the application and making documentation changes.}
\resumeItemListEnd
\resumeSubHeadingListEnd
%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{\href{https://github.com/Rohith-Raju/Crux}{Crux}}{(Work in Progress) Crux is a C++ implementation of the Lox interpreter by following the principles used in the Crafting Interpreters book written by Bob Nystrom.
    }
    \resumeSubItem{\href{https://github.com/Rohith-Raju/LinkedList}{LinkedList}}{This project consits of templated version of linear linked list that mimics the style used in C++ standard template library. This project was done to learn, 
    understand and practice concepts specifically tied to C++.}
    \resumeSubItem{\href{https://www.jetir.org/view?paper=JETIR2306084}{Telemetry Observability For Self-Piloted Robot}}
    {A self-piloted robot with infrared sensors follows a  predefined path that is marked with a 
    black line on a contrasting white colour, using sensor data to make decisions. Journey data is sent to a database for
    realtime analysis.}
    \resumeSubItem{\href{https://triptalk-production.web.app/home}{TripTalk}}
    {TripTalk is a  web application built with react with allows users to create travel blogs.}
    \resumeSubItem{\href{https://github.com/rohith-raju/Reva-results}{Reva Results}}
    {A python and xpath web scraper which scrapes and formats the results site and displays the marks of a student}
  \resumeSubHeadingListEnd

  \section{Talks and Presentation}
  \resumeSubHeadingListStart
    \resumeSubheading
      {The Falco Playground: A Cocktail of WebAssembly and Runtime Security}{ Chicago, Illinois}
      { Working of falco and falco playground } {Youtube:\href{https://youtu.be/imvDmhLRFRo?feature=shared}{Link} {Slides:\href{https://docs.google.com/presentation/d/17sfxAgLnr4ehiXhuEd9y9gcrihwq1bPD6al1aj0ZKao/edit?usp=sharing}{Link}}}
    \resumeSubheading
      {Building a Docker Extension from scratch }{ Microsoft Reactor,Bangalore}
      {Inner workings of Docker extensions and building a sample app}{Slides:\href{https://docs.google.com/presentation/d/1eOYVtNRt8SeyemGuL_uZIlJyrxOAl_gprnx9v2aZAUM/edit?usp=sharing}{Link}   Hilights:\href{https://drive.google.com/drive/folders/1Cc1-D9oDcjYr8iZqH8Dr1RG95xvYg9NM?usp=sharing}{Link}}
  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Languages}{: C++, Python, Javascript, Go }
     \hfill
     \textbf{Technologies}{: React, Node, Typescript , GCP , MongoDb, Aws}
   }
 \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
